\documentclass[11pt,letterpaper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{purple}

\usepackage[scale=0.80]{geometry}
\addtolength{\voffset}{-3.5em}
\addtolength{\textheight}{7em}


\name{James}{Harbour}
\title{Resume}
\phone{+1~(205)~876~4085}
\email{james.h.harbour@gmail.com}
\homepage{jameshharbour.net}
\social{gtr8rh@virginia.edu}
\social[github]{kyrem1}
% \lfoot{\emph{Last updated \today}}

\sethintscolumnlength{1cm}


\begin{document}
\makecvtitle % Print the CV title
\vspace*{-3.5em}

% \cventry{Grade}{CourseID}{CourseName}{Semester}{Professor}%
%    {Description \\ \emph{Textbook: }TextAuthor \emph{TextName}.}

%\begin{center}
%  %I am a mathematics and computer science double major at the University of Virginia with a comprehensive undergraduate and graduate-level mathematics background. My primary interests are in operator algerbas and noncommutative geometry.
%
%\vspace{1.0em}
%  Following my PhD, I plan to pivot towards the financial sector with a focus on quantitative finance and algorithmic trading.
%\end{center}

\section{Education}

\begin{itemize}
  \item \textbf{Class of 2025 at the University of Virginia}, Mathematics and Computer Science double major
  \item Completed the undergraduate requirements for mathematics major during high school.
  \item Completed the UVA mathematics PhD curriculum as a first year student.
  \item \textbf{Graduate level courses}: Random Walks on Groups, Functional Analysis, Measure Theory, Complex Analysis, Differential Topology, Algebraic Topology I \& II, Algebraic Geometry, Algebra I \& II
\end{itemize}



\section{Mathematics Experience}

\cventry{2023}{UChicago REU}{}{Full participant}{Researching $ s $-Perimiter and Nonlocal Potential Theory}{}
\cventry{2022}{UVA Research}{}{I took an intensive one-on-one reading and research course in operator algebras with Dr. Benjamin Hayes. Living expenses were covered by a grant (see below). }{}{}



\section{Selected Talks}

\cventry{4/23}{Maximal rigidity for $L^2$-cohomology of Groups and Beyond}{UVA Operator Theory seminar}{}{}{} 
\cventry{11/22}{Index Rigidity for type-$ II_1 $ Subfactors}{UVA Operator Theory seminar}{}{}{}
\cventry{11/22}{Construction and examples of the von Neumann dimension of Hilbert modules}{UVA Operator Theory seminar}{}{}{}

\section{Conferences}
\cventry{05/23}{Great Plains Operator Theory Symposium (GPOTS)}{Ohio State University}{}{}{}
\cventry{05/23}{Noncommutative Geometry and Operator Algebras (NCGOA) Spring Institute}{Vanderbilt University}{}{}{}
\cventry{01/23}{Joint Math Meetings}{Boston}{}{}{}
\cventry{10/22}{East Coast Operator Algebras Symposium}{Michigan State University}{}{}{}
\cventry{06/22}{Thematic Program in p-adic L-functions and Eigenvarieties}{University of Notre Dame}{}{}{}
 


\section{Financial Experience}
\begin{itemize}
  \item \textbf{Member of UVA's Alternative Investment Fund}\quad An investment club managing a portfolio of $ \$60,000 $ AUM with both systematic and discretionary trading strategies. Rigorous selection process with multiple interviews and a $ 3\% $ acceptance rate. 
\end{itemize}

\section{Programming Experience}
\textbf{Proficient In} Java, C, C++, Assembly, Python, Javascript, \LaTeX, SageMath, Mathematica. I have taken courses in algorithmic economics, computer architectures, and machine learning.

\section{Honors and Awards}
\begin{itemize}
  \item Various Grants/Funding/Travel (see my website for more info)
  \begin{itemize}
    \item \$2000 Supporting summer research in operator algebras alongside Dr. Benjamin Hayes.
    \item \$500 For travel to the Notre Dame workshop in Elliptic Curves and Modular Forms
    \item \$1000 Supporting travel fees to attend the East Coast Operator Algebras Seminar. 
    \item \$1500 Supporting travel fees to attend the Joint Mathematics Meetings
  \end{itemize}
  \item Mathematics PhD Qualifying Exams - Passed Real \& Complex Analysis Exams (as a freshman)

  % TODO

 % \item Echols Scholar, University of Virginia
 % \begin{itemize}
 %   \item Selected for Honors Program (5\% of incoming freshman), waives gen-ed requirements.
 % \end{itemize}
  
\end{itemize}

\end{document}
