\documentclass[12pt,letterpaper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{purple}

\usepackage[scale=0.75]{geometry}
\addtolength{\voffset}{-3.5em}
\addtolength{\textheight}{7em}

\quote{``Find what you love and let it kill you''
--- Charles Bukowski}

\name{James}{Harbour}
\title{Resume}
\phone{+1~(205)~876~4085}
\email{james.h.harbour@gmail.com}
\social{gtr8rh@virginia.edu}
\social[github]{kyrem1}
% \lfoot{\emph{Last updated \today}}

\sethintscolumnlength{1cm}


\begin{document}

\makecvtitle % Print the CV title
\vspace*{-1.5em}


% \cventry{Grade}{CourseID}{CourseName}{Semester}{Professor}%
%    {Description \\ \emph{Textbook: }TextAuthor \emph{TextName}.}

\begin{center}
  I am a second year mathematics and computer science double major at the University of Virginia with a comprehensive undergraduate and graduate-level mathematics background. My primary interests are in operator algerbas and noncommutative geometry. \\
\vspace{1.5em}
  Following my PhD, I plan to pivot towards industry with a focus on quantitative finance and algorithmic trading.
\end{center}

\section{Mathematics Experience}

\begin{itemize}
  \item \textbf{pre - UVA}\quad Through concurrent dual enrollment at the University of South Florida during high school, I completed the majority of courses in a mathematics major as well as a variety of graduate-level courses.
  \item \textbf{UVA - 1st Year}\quad Took the same mathematics courseload as UVA's 1st year mathematics PhD students (plus more courses). Passed the analysis (real \& complex) PhD qualifying exams.
  \item \textbf{UVA - 2nd Year}\quad Spent the summer at UVA doing a one-on-one reading course with one of my professors. Living expenses were covered by a \$2000 grant from the mathematics department. Currently I am taking three 2nd year PhD-level mathematics courses. I am also a member of the UVA operator theory seminar for graduate students
\end{itemize}


\section{Programming Experience}
\textbf{Proficient In}\quad Java, C++, Python, Javascript (see my github above) \\
\textbf{Using scientific-computing software (SageMath, Mathematica)}\quad level: medium \\
\textbf{Using document markup software (\LaTeX, Office Suite)}\quad level: advanced \\
\textbf{Using Linux}\quad level: medium. (I currently run Arch-Linux on my main laptop)

\section{Honors and Awards}
\begin{itemize}
  \item Obtained \$2000 grant from the UVA mathematics department.
  \begin{itemize}
    \item Supported summer research in operator algebras alongside Dr. Benjamin Hayes.
  \end{itemize}
  \item Mathematics PhD Qualifying Exams
  \begin{itemize}
    \item I took the Real and Complex analysis qualifying exams for upcoming 2nd year PhD students and successfully passed both.
  \end{itemize}
  \item College Science Scholar, University of Virginia
  \begin{itemize}
    \item Selected as one of 18 undergraduates for a research-oriented science-mentoring program.
  \end{itemize}

  % TODO

  \item Echols Scholar, University of Virginia
  \begin{itemize}
    \item Selected for Honors Program (5\% of incoming freshman), waives general education requirements.
  \end{itemize}
  
\end{itemize}

\end{document}
